Bird beak's elaboration and innovation

### 2022-08-01 Analysis/03-Elaboration_innovation_analysis.Rmd
Added curves comparisons
Update 03-Elaboration_innovation_analysis.Rmd

## Group info
suborders <- lapply(results$suborder_results_phylo$position$subsets, function(x, data) list(species = rownames(data)[c(x$elements)]), data = results$suborder_results_phylo$position$matrix[[1]])
families <- lapply(results$family_results_phylo$position$subsets, function(x, data) list(species = rownames(data)[c(x$elements)]), data = results$family_results_phylo$position$matrix[[1]])
## Adding the colours
load("../Data/Processed/tip_colours_suborders.rda")
load("../Data/Processed/tip_colours_families.rda")
add.col <- function(one_order, one_col) {
    one_order$col <- one_col
    return(one_order)
}
suborders <- mapply(add.col, one_order = suborders[1:8][match(names(suborders[1:8]), names(tip_colours_suborders))], one_col = as.list(tip_colours_suborders), SIMPLIFY = FALSE)
families <- mapply(add.col, one_order = families[1:27][match(names(families[1:27]), names(tip_colours_families))], one_col = as.list(tip_colours_families), SIMPLIFY = FALSE)

>>>>

## Group info
suborders <- lapply(results$suborder_results_phylo$position$subsets, function(x, data) list(species = rownames(data)[c(x$elements)]), data = results$suborder_results_phylo$position$matrix[[1]])
families <- lapply(results$family_results_phylo$position$subsets, function(x, data) list(species = rownames(data)[c(x$elements)]), data = results$family_results_phylo$position$matrix[[1]])
## Adding the colours
load("../Data/Processed/tip_colours_passeriformes_suborder.rda")
load("../Data/Processed/tip_colours_passeriformes_family.rda")
add.col <- function(one_order, one_col) {
    one_order$col <- one_col
    return(one_order)
}
suborders <- mapply(add.col, one_order = suborders[1:8][match(names(suborders[1:8]), names(tip_colours_passeriformes_suborder))], one_col = as.list(tip_colours_suborders), SIMPLIFY = FALSE)
families <- mapply(add.col, one_order = families[1:27][match(names(families[1:27]), names(tip_colours_passeriformes_family))], one_col = as.list(tip_colours_families), SIMPLIFY = FALSE)
